---
title: 'Grappling with the "Body awareness" scale'
subtitle: 'Last updated 2018-04-07'
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r, include = FALSE}
# set working director
# setwd("/Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_packets/packets123/")

# load packages
library(tidyverse)
library(rms)
library(ggdendro)
library(psych)

# load question key (including manual reverse-coding)
question_key <- read.csv("//Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_packets/packets123/packets123_question_key_byhand.csv")

# load data (reverse-coded)
d_long <- read_csv("//Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_packets/packets123/packets123_data_byquestion_long.csv") %>%
  mutate(ctry = factor(ctry, 
                       levels = c("us", "ghana", "thailand", "china", "vanuatu")))
d_long_subscale <- read_csv("//Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_packets/packets123/packets123_data_bysubscale_long.csv") %>%
  mutate(ctry = factor(ctry, 
                       levels = c("us", "ghana", "thailand", "china", "vanuatu")))

# load data (before reverse-coding)
d_all <- read.csv("//Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_packets/packets123/packets123_data.csv")

# make custom functions
round2 <- function(x) {format(round(x, 2), digits = 2)}
```

Here we look at the "sensory seeking" scale (Brown et al.; Packet 2) in detail.

# Differences across fieldsites

## Mean scores by site

First, let's look at scores for participants in each site:

```{r, include = F}
d_long_subscale_boot <- d_long_subscale %>%
  filter(!is.na(sum_score)) %>%
  group_by(ctry, packet, subscale) %>%
  do(data.frame(rbind(smean.cl.boot(.$sum_score)))) %>%
  ungroup() %>%
  filter(subscale != "attn") %>%
  left_join(d_long_subscale %>%
              filter(!is.na(sum_score)) %>%
              count(ctry, packet, subscale)) %>%
  mutate(packet = paste("packet", packet),
         ctry = factor(ctry,
                       levels = c("us", "ghana", 
                                  "thailand", "china", "vanuatu")),
         subscale = 
           factor(subscale,
                  levels = c("exwl", 
                             "exwl_extra",
                             "dse_01to14", 
                             "dse_15to16", 
                             "spev", 
                             "sen_sensory_seeking", 
                             "sen_body_awareness", 
                             "sen_trait_metamood",
                             "her2_hallucination",
                             "invo_VISQ_dialogic_speech", 
                             "invo_VISQ_inner_speech",
                             "invo_VISQ_eval_motiv_inner_speech",
                             "invo_hardy_bentall",
                             "her_posey_losch",
                             "enco_lewicki",
                             "meta_van_elk",
                             "tat_confidence",
                             "tat_positive_beliefs",
                             "tat_cognitive",
                             "tat_uncontrollability",
                             "tat_need_control",
                             "minw_mental_states",
                             "minw_life_events",
                             "minw_inanimate",
                             "minw_selves_souls_world",
                             "minw_epistemic"),
                  labels = c("absorption (tellegen)", 
                             "absorption (extra)",
                             "daily spiritual experiences (#1-14)",
                             "daily spiritual experiences (#15-16)",
                             "spiritual events", 
                             "sensory seeking",
                             "body awareness", 
                             "attention to feelings",
                             "hallucination", 
                             "VISQ: dialogic speech",
                             "VISQ: inner speech",
                             "VISQ: evaluative",
                             "inner speech",
                             "hearing events",
                             "encoding style",
                             "mind metaphors",
                             "metacog.: lack of cognitive confidence",
                             "metacog.: positive beliefs re: worrying",
                             "metacog.: cognitive self-consciousness",
                             "metacog.: uncontrollability/danger",
                             "metacog.: need to control thoughts",
                             "dualism: mental states",
                             "dualism: life events",
                             "dualism: inanimate consciousness",
                             "dualism: minds, selves, & world",
                             "dualism: epistemology")))
```

```{r, fig.width = 3, fig.asp = 0.9}
ggplot(d_long_subscale_boot %>%
         filter(subscale == "body awareness"),
       aes(x = ctry, y = Mean)) +
  # geom_hline(aes(yintercept = 0), lty = 2, color = "black") +
  # geom_hline(aes(yintercept = 36), lty = 2, color = "black") +
  geom_point(data = d_long_subscale %>%
               filter(subscale == "sen_body_awareness",
                      !is.na(sum_score)),
             aes(y = sum_score, color = ctry),
             position = position_jitter(width = 0.3, height = 0),
             alpha = 0.3, size = 1) +
  geom_pointrange(aes(ymin = Lower, ymax = Upper)) +
  geom_text(aes(label = paste0("(n=", n, ")"), y = Lower), 
            size = 2, nudge_x = 0.15, hjust = 0) +
  # scale_x_discrete(expand = c(0, 1)) +
  scale_y_continuous(limits = c(-36.5, 36.5), breaks = seq(-100, 100, 10)) +
  scale_color_brewer(palette = "Dark2") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none") +
  labs(title = "Mean body awareness scores by site (Shields et al.)",
       subtitle = "A higher score indicates more endorsements of 'sensory seeking' (range: -36 to 36)\nError bars are bootstrapped 95% confidence intervals",
       x = "Site", color = "Site",
       y = "Mean score")
```

Note that this plot includes both average scores for each site (in black), and individual scores for all of the participants in that site (small, colorful points in the background, which are "jittered" around a little so that you can see them all).

Looks like people in different sites responded somewhat differently to this scale, but the differences are pretty subtle. Participants in Vanuatu responded substantially more positively; participants in China and maybe the US somewhat more neutrally/negatively. 

Now let's look at these differences in more detail using the "raw data" for individual questions, rather than these subscale scores.

## Responses by question, by site

```{r, fig.width = 10, fig.asp = 0.7}
d_plot <- d_long %>%
  filter(question %in% c("sen_15", "sen_16", "sen_17", "sen_18", "sen_19",
                         "sen_20", "sen_21", "sen_22", "sen_23", "sen_24",
                         "sen_25", "sen_26", "sen_27", "sen_28", "sen_29",
                         "sen_30", "sen_31", "sen_32", "sen_33"),
         !grepl("attn", question)) %>%
  left_join(question_key %>%
              distinct(question_label_universal, 
                       question_text,
                       byhand_coding,
                       byhand_subscale) %>%
              rename(question = question_label_universal,
                     coding = byhand_coding,
                     subscale = byhand_subscale)) %>%
  distinct() %>%
  mutate(response = response * coding, # undo reverse-coding
         coding = factor(coding,
                         levels = c("-1", "1"),
                         labels = c("(REVERSED)", "")),
         question_text_short = gsub('(.{1,30})(\\s|$)',
                                    '\\1\n',
                                    paste0(question,
                                           ": ",
                                           substr(question_text,
                                                  start = 1, stop = 10000),
                                           # "...",
                                           coding))) %>%
  count(ctry, question_text_short, response) %>%
  spread(response, n) %>%
  mutate_at(vars(`-2`:`2`), 
            funs(replace(., is.na(.), 0))) %>%
  arrange(ctry, `-2`) %>%
  rownames_to_column("order") %>%
  mutate(order = as.numeric(order),
         agree_n = `1` + `2`,
         total_n = `-2` + `-1` + `0` + `1` + `2`) %>%
  gather(response, n, c(`-2`, `-1`, `0`, `1`, `2`)) %>%
  mutate(response = factor(response,
                           levels = c("-2", "-1", "0", "1", "2")),
         ctry = factor(ctry,
                       levels = c("us", "ghana", "thailand", 
                                  "china", "vanuatu"),
                       labels = c("US", "Ghana", "Thailand", 
                                  "China", "Vanuatu"))) %>%
  distinct()

adjust <- 15

ggplot(d_plot %>%
         mutate(response = factor(response,
                                  labels = c("Strongly disagree", "Disagree", 
                                             "Neither agree nor disagree",
                                             "Agree", "Strongly agree"))),
       aes(x = reorder(question_text_short, desc(question_text_short)),
           # x = reorder(question_text_short, desc(order)),
           y = n, fill = response)) +
  facet_grid(. ~ ctry, scales = "free", space = "free") +
  geom_bar(position = position_stack(), stat = "identity", 
           color = "black", size = 0.2) +
  geom_text(data = d_plot %>% 
              distinct(ctry, question_text_short, order, 
                       agree_n, total_n),
            aes(y = max(d_plot$total_n) + adjust, fill = NULL,
                label = paste0(round(agree_n/total_n, 2)*100, "%")), 
            size = 3, hjust = 1) +
  scale_y_continuous(limits = c(0, max(d_plot$total_n) + adjust)) +
  scale_fill_brewer(palette = "PRGn") +
  theme_bw() +
  labs(title = "Responses to 'Body awareness' (Shields et al.) scale items",
       subtitle = "% corresponds to responses of 'Agree' or 'Strongly agree' (green)",
       x = "", y = "Count of responses", fill = "Response") +
  theme(legend.position = "top",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  # theme(axis.text.x = element_text(angle = 90, hjust = 1))
  coord_flip()

rm(adjust)
```

**NOTE**: This scale has **1 reverse-coded item** (`sen_24`), which is *not* reverse-coded in this plot - i.e., if people selected "Disagree" for this item, it's plotted here as "Disagree." (For the previous plots of overall "scores," this item was reverse-coded.)

As always, lots to chew on here. Off the top of my head, a few things stand out:

- More use of the neutral midpoint in TH but not CH, this time.
- At a glance, it seems like people in VT used the "disagree" end of the scale (purple) maybe a little less than others, and hardly ever used the most extreme negative endpoint ("Strongly disagree")... though let's also look at this at an individual level (below).
- People in TH agreed exceptionally strongly with the item, "I always know when I've exerted myself to the point where I'll be sore the next day" (`sen_17`). Interesting! What do you make of this, **Felicity**?
- The flu seemed to come out of nowhwere for participants in CH (`sen_19`).
- Participants in GH and VT reported being more attuned to the difference between tiredness due to hunger vs. sleep (`sen_21`).

...and so much more.

Again, **Josh**, you've gotta take a look at these with an eye toward a ratio! Maybe we should fold them into the "ratio of senses" doc...

# Distribution of responses for individual participants, by site

Another thing we might be interested in is how individual participants responded: Were there people who said yes to everything, or no to everything? How do these distributions of responses differ across participants in different sites?

Let's take a look:

```{r, fig.width = 6, fig.asp = 1}
d_long %>%
  filter(question %in% c("sen_15", "sen_16", "sen_17", "sen_18", "sen_19",
                         "sen_20", "sen_21", "sen_22", "sen_23", "sen_24",
                         "sen_25", "sen_26", "sen_27", "sen_28", "sen_29",
                         "sen_30", "sen_31", "sen_32", "sen_33"),
         !grepl("attn", question), !is.na(response)) %>%
  left_join(question_key %>%
              distinct(question_label_universal, 
                       question_text,
                       byhand_coding,
                       byhand_subscale) %>%
              rename(question = question_label_universal,
                     coding = byhand_coding,
                     subscale = byhand_subscale)) %>%
  distinct() %>%
  mutate(response = factor(response),
         coding = factor(coding,
                         levels = c("-1", "1"),
                         labels = c("(REVERSED)", "")),
         question_text_short = gsub('(.{1,130})(\\s|$)',
                                    '\\1\n',
                                    paste0(substr(question_text,
                                                     start = 1, stop = 10000),
                                              # "...",
                                              coding)),
         subscale = factor(subscale, 
                           labels = c("Body awareness (Shields et al.)"))) %>%
  distinct() %>%
  count(ctry, subscale, subj, response) %>%
  spread(response, n) %>%
  mutate_at(vars(c(`-2`, `-1`, `0`, `1`, `2`)), funs(replace(., is.na(.), 0))) %>%
  mutate(total_n = `-2` + `-1` + `0` + `1` + `2`,
         prop_n2 = `-2`/total_n,
         prop_n1 = `-1`/total_n,
         prop_n0 = `0`/total_n,
         prop_p1 = `1`/total_n,
         prop_p2 = `2`/total_n,
         ctry = factor(ctry,
                       levels = c("us", "ghana", "thailand", 
                                  "china", "vanuatu"),
                       labels = c("US", "Ghana", "Thailand", 
                                  "China", "Vanuatu"))) %>%
  distinct() %>%
  select(-c(`-2`, `-1`, `0`, `1`, `2`)) %>%
  gather(response, prop, starts_with("prop")) %>%
  mutate(response = factor(response,
                           levels = c("prop_n2", "prop_n1", "prop_n0",
                                      "prop_p1", "prop_p2"),
                           labels = c("Strongly disagree", "Disagree", 
                                      "Neither agree nor disagree",
                                      "Agree", "Strongly agree"))) %>%
  ggplot(aes(x = prop, fill = ctry)) +
  facet_grid(response ~ ctry, scales = "free", space = "free") +
  geom_histogram(binwidth = 1/14) +
  scale_x_continuous(breaks = seq(0, 1, 0.25)) +
  scale_y_continuous(breaks = seq(0, 100, 10)) +
  scale_fill_brewer(palette = "Dark2") +
  theme_bw() +
  labs(title = "Distributions of how many times participants endorsed each response option for the 'Body awareness' (Shields et al.) scale items",
       x = "Proportion of responses (at the individual participant level)", y = "Count of participants", fill = "Site") +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))
```

Again, lots to chew on here, including:

- The vast majority of participants across sites - especially in the US and TH - *never* used the most extreme negative response option, "Strongly disagree".
- This general pattern is also true (though less extreme) for the most extreme positive response option, "Strongly agree", particularly in the US and GH.
- There were a handful of people in VT who said "Strongly agree" for every (or almost every) question - but just a few. This didn't seem to happen anywhere else.
- Nobody said "Strongly disagree" for every (or almost every) question.
- There were a handful of people everywhere, but particularly in GH and CH, who chose the neutral response ("Neither agree nor disagree") for every (or almost every) question - but just a few. (Up your alley re: neutrality vs. contradiction, **Emily**.)

Again, lots to sort through here.

Just for fun, here's another way to look at the same data, overlaying the density distributions for each site on top of each other to see where they seem to be similar/different:

```{r, fig.width = 3, fig.asp = 3}
d_long %>%
  filter(question %in% c("sen_15", "sen_16", "sen_17", "sen_18", "sen_19",
                         "sen_20", "sen_21", "sen_22", "sen_23", "sen_24",
                         "sen_25", "sen_26", "sen_27", "sen_28", "sen_29",
                         "sen_30", "sen_31", "sen_32", "sen_33"),
         !grepl("attn", question), !is.na(response)) %>%
  left_join(question_key %>%
              distinct(question_label_universal, 
                       question_text,
                       byhand_coding,
                       byhand_subscale) %>%
              rename(question = question_label_universal,
                     coding = byhand_coding,
                     subscale = byhand_subscale)) %>%
  distinct() %>%
  mutate(coding = factor(coding,
                         levels = c("-1", "1"),
                         labels = c("(REVERSED)", "")),
         question_text_short = gsub('(.{1,130})(\\s|$)',
                                    '\\1\n',
                                    paste0(substr(question_text,
                                                     start = 1, stop = 10000),
                                              # "...",
                                              coding)),
         subscale = factor(subscale, 
                           labels = c("Sensory seeking (Brown et al.)"))) %>%
  distinct() %>%
  count(ctry, subscale, subj, response) %>%
  spread(response, n) %>%
  mutate_at(vars(c(`-2`, `-1`, `0`, `1`, `2`)), funs(replace(., is.na(.), 0))) %>%
  mutate(total_n = `-2` + `-1` + `0` + `1` + `2`,
         prop_n2 = `-2`/total_n,
         prop_n1 = `-1`/total_n,
         prop_n0 = `0`/total_n,
         prop_p1 = `1`/total_n,
         prop_p2 = `2`/total_n,
         ctry = factor(ctry,
                       levels = c("us", "ghana", "thailand", 
                                  "china", "vanuatu"),
                       labels = c("US", "Ghana", "Thailand", 
                                  "China", "Vanuatu"))) %>%
  distinct() %>%
  select(-c(`-2`, `-1`, `0`, `1`, `2`)) %>%
  gather(response, prop, starts_with("prop")) %>%
  mutate(response = factor(response,
                           levels = c("prop_n2", "prop_n1", "prop_n0",
                                      "prop_p1", "prop_p2"),
                           labels = c("Strongly disagree", "Disagree", 
                                      "Neither agree nor disagree",
                                      "Agree", "Strongly agree"))) %>%
  ggplot(aes(x = prop, fill = ctry)) +
  facet_grid(response ~ ., scales = "free", space = "fixed") +
  geom_density(alpha = 0.3) +
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.25)) +
  scale_fill_brewer(palette = "Dark2") +
  theme_bw() +
  labs(title = "Distributions of how many times participants endorsed each\nresponse option for the 'Body awareness' (Shields et al.) scale items",
       x = "Proportion of responses (at the individual participant level)", y = "Count of participants", fill = "Site") +
  theme(legend.position = "top",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))
```

