---
title: 'Packet 2: Relationships among scales'
subtitle: 'Last updated 2018-04-07'
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r, include = FALSE}
# set working director
# setwd("/Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_packets/packets123/")

# load packages
library(tidyverse)
library(rms)
library(ggdendro)

# load question key (including manual reverse-coding)
question_key <- read.csv("//Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_packets/packets123/packets123_question_key_byhand.csv")

# load data
d_long <- read_csv("//Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_packets/packets123/packets123_data_byquestion_long.csv") %>%
  mutate(ctry = factor(ctry, 
                       levels = c("us", "ghana", "thailand", 
                                  "china", "vanuatu"))) %>%
  filter(packet == 2)

d_long_subscale <- read_csv("//Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_packets/packets123/packets123_data_bysubscale_long.csv") %>%
  mutate(ctry = factor(ctry, 
                       levels = c("us", "ghana", "thailand", 
                                  "china", "vanuatu")),
                  subscale = 
           factor(subscale,
                  levels = c("exwl", 
                             "exwl_extra",
                             "dse_01to14", 
                             "dse_15to16", 
                             "spev", 
                             "sen_sensory_seeking", 
                             "sen_body_awareness", 
                             "sen_trait_metamood",
                             "her2_hallucination",
                             "invo_VISQ_dialogic_speech", 
                             "invo_VISQ_inner_speech",
                             "invo_VISQ_eval_motiv_inner_speech",
                             "invo_hardy_bentall",
                             "her_posey_losch",
                             "enco_lewicki",
                             "meta_van_elk",
                             "tat_confidence",
                             "tat_positive_beliefs",
                             "tat_cognitive",
                             "tat_uncontrollability",
                             "tat_need_control",
                             "minw_mental_states",
                             "minw_life_events",
                             "minw_inanimate",
                             "minw_selves_souls_world",
                             "minw_epistemic"),
                  labels = c("absorption (tellegen)", 
                             "absorption (extra)",
                             "daily spiritual experiences (#1-14)",
                             "daily spiritual experiences (#15-16)",
                             "spiritual events", 
                             "sensory seeking",
                             "body awareness", 
                             "attention to feelings",
                             "hallucination", 
                             "VISQ: dialogic speech",
                             "VISQ: inner speech",
                             "VISQ: evaluative",
                             "inner speech",
                             "hearing events",
                             "encoding style",
                             "mind metaphors",
                             "metacog.: lack of cognitive confidence",
                             "metacog.: positive beliefs re: worrying",
                             "metacog.: cognitive self-consciousness",
                             "metacog.: uncontrollability/danger",
                             "metacog.: need to control thoughts",
                             "dualism: mental states",
                             "dualism: life events",
                             "dualism: inanimate consciousness",
                             "dualism: minds, selves, & world",
                             "dualism: epistemology"))) %>%
  filter(packet == 2)
d_wide_subscale <- d_long_subscale %>%
  spread(subscale, sum_score)

# effect-code site
contrasts(d_wide_subscale$ctry) <- cbind(ghana = c(-1, 1, 0, 0, 0),
                                         thailand = c(-1, 0, 1, 0, 0),
                                         china = c(-1, 0, 0, 1, 0),
                                         vanuatu = c(-1, 0, 0, 0, 1))

# make custom functions
round2 <- function(x) {format(round(x, 2), digits = 2)}
```

This is an exploration of the relationships among scales included in Packet 2.

# Correlation matrix

First, let's look at the overall correlationships among scores on the various scales included in Packet 2. (These are individual participant-level correlations):

```{r fig.width = 3, fig.asp = 1}
d_long_subscale %>%
  filter(packet == 2, !is.na(sum_score), !is.na(subscale)) %>%
  spread(subscale, sum_score) %>%
  select(-c(ctry, wher, recr, whoc)) %>%
  mutate(subj = paste(subj, packet, version, sep = "_")) %>%
  select(-packet, -version) %>%
  distinct() %>%
  remove_rownames() %>%
  column_to_rownames("subj") %>%
  cor(use = "pairwise.complete.obs") %>%
  # # corrplot version:
  # corrplot::corrplot(method = "color", tl.col = "black",
  #                    addCoef.col = "black", order = "hclust",
  #                    col = RColorBrewer::brewer.pal(n = 11, name = "PRGn"),
  #                    title = "\nPACKET 2: correlations among subscales")

  # ggplot version:
  data.frame() %>%
  rownames_to_column("subscaleA") %>%
  gather(subscaleB, cor, -subscaleA) %>%
  ggplot(aes(x = subscaleA, y = subscaleB, fill = cor, label = round2(cor))) +
  geom_tile() +
  geom_text(size = 3) +
  scale_fill_distiller(guide = guide_colorbar(barheight = 6),
                       palette = "RdYlBu", limits = c(-1, 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "PACKET 2: correlations among subscales",
       subtitle = "using pairwise complete observations",
       x = "",
       y = "")
```

From this, we see that several of the scales included in Packet 2 were positively correlated with each other. Unsurprisingly, many of the "inner speech" subscales were positively correlated (all of the VISQ subscales and the Hardy/Bentall inner speech scale). But we also see some intriguing correlations among the inner speech scales and the "hallucination" scale (among other things). Let's check these relationships out in more detail!

# Inner speech and "hallucinations"

## ...as measured by Hardy/Bentall

Here's a test for the overall correlation between inner speech as measured by the Hardy/Bentall scale, and hallucination-like experiences as measured by the Alderson-Day scale:

```{r}
cor1 <- with(d_wide_subscale, cor.test(`inner speech`, hallucination)); cor1
```

Inner speech (as measured by Hardy/Bentall) was significantly positively correlated with reported hallucination-like events ($r$ = `r round2(cor1$estimate)`, $p$ = `r ifelse(cor1$p.value < 0.001, "<0.001", format(round(cor1$p.value, 3), digits = 3))`), accounting for approximately `r round(cor1$estimate^2 * 100)`% of the variance in reported hallucinations.

Now let's take a look at what's going on in each site with a regression analysis:

```{r, results = "asis"}
r1 <- lm(hallucination ~ `inner speech` * ctry, 
         d_wide_subscale %>% 
           mutate(`inner speech` = scale(`inner speech`, scale = F)))

r1_coef <- summary(r1)$coefficients %>%
  data.frame() %>%
  rownames_to_column("param") %>%
  rename(b = Estimate, se = Std..Error, t = t.value, p = Pr...t..) %>%
  mutate_at(vars(b, se, t), funs(round2)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001",
                    format(round(p, 3), digits = 3)),
         param = factor(param,
                        levels = c("(Intercept)", 
                                   "ctryghana", 
                                   "ctrythailand",
                                   "ctrychina", 
                                   "ctryvanuatu", 
                                   "`inner speech`",
                                   "`inner speech`:ctryghana", 
                                   "`inner speech`:ctrythailand", 
                                   "`inner speech`:ctrychina", 
                                   "`inner speech`:ctryvanuatu"),
                        labels = c("baserate (overall)", 
                                   "baserate (ghana vs. overall)",
                                   "baserate (thailand vs. overall)",
                                   "baserate (china vs. overall)",
                                   "baserate (vanuatu vs. overall)",
                                   "HB inner speech (overall)",
                                   "HB inner speech (ghana vs. overall)",
                                   "HB inner speech (thailand vs. overall)",
                                   "HB inner speech (china vs. overall)",
                                   "HB inner speech (vanuatu vs. overall)"))) %>%
  arrange(param) %>%
  column_to_rownames("param")

knitr::kable(r1_coef)
```

These results indicate that there was a significant positive relationship between inner speech (as measured by Hardy/Bentall) and reported hallucination-like events, collapsing across sites ($b$ = `r r1_coef["HB inner speech (overall)", "b"]`, $p$ = `r r1_coef["HB inner speech (overall)", "p"]`). The relationship between inner voice and hallucinations was somewhat weaker among participants in Thailand and Vanuatu (Thailand: $b$ = `r r1_coef["HB inner speech (thailand vs. overall)", "b"]`, $p$ = `r r1_coef["HB inner speech (thailand vs. overall)", "p"]`; Vanuatu: $b$ = `r r1_coef["HB inner speech (vanuatu vs. overall)", "b"]`, $p$ = `r r1_coef["HB inner speech (vanuatu vs. overall)", "p"]`).

Note also that this test picked up on some differences in the baserates for reporting hallucination-like events (controlling for the relationships described above): Participants in Ghana and Thailand seem to have reported fewer than average of these kinds of events (Ghana: $b$ = `r r1_coef["baserate (ghana vs. overall)", "b"]`, $p$ = `r r1_coef["baserate (ghana vs. overall)", "p"]`; Thailand: $b$ = `r r1_coef["baserate (thailand vs. overall)", "b"]`, $p$ = `r r1_coef["baserate (thailand vs. overall)", "p"]`).

Here's a visualization of these relationships:

```{r, fig.width = 4, fig.asp = 0.375}
d_wide_subscale %>%
  filter(!is.na(`inner speech`), !is.na(hallucination)) %>%
  ggplot(aes(x = `inner speech`, # x = exwl_cent,
             y = hallucination, color = ctry)) +
  facet_grid(~ ctry) +
  geom_point(size = 1, alpha = 0.5) +
  geom_smooth(method = "lm", color = "black") +
  # geom_line(data = fortify(r1), aes(x = exwl_cent, y = .fitted), color = "black") +
  scale_color_brewer(palette = "Dark2") +
  scale_x_continuous(limits = c(-20, 20), breaks = seq(-100, 100, 5)) +
  scale_y_continuous(limits = c(0, 27), breaks = seq(-100, 100, 2)) +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(title = "Relationship between inner speech (Hardy & Bentall) & hallucinations, by site",
       color = "Site",
       x = "Inner speech (Hardy & Bentall)",
       y = "Hallucinations (Alderson-Day)")
```

## ...as measured by the "inner speech" subscale of the VISQ

Here's a test for the overall correlation between inner speech as measured by the VISQ "inner speech" subscale, and hallucination-like experiences as measured by the Alderson-Day scale:

```{r}
cor2 <- with(d_wide_subscale, cor.test(`VISQ: inner speech`, hallucination)); cor2
```

Inner speech (as measured by VISQ) was significantly positively correlated with reported hallucination-like events ($r$ = `r round2(cor2$estimate)`, $p$ = `r ifelse(cor2$p.value < 0.001, "<0.001", format(round(cor2$p.value, 3), digits = 3))`), accounting for approximately `r round(cor2$estimate^2 * 100)`% of the variance in reported hallucinations.

Now let's take a look at what's going on in each site with a regression analysis:

```{r, results = "asis"}
r2 <- lm(hallucination ~ `VISQ: inner speech` * ctry, 
         d_wide_subscale %>% 
           mutate(`VISQ: inner speech` = scale(`VISQ: inner speech`, scale = F)))

r2_coef <- summary(r2)$coefficients %>%
  data.frame() %>%
  rownames_to_column("param") %>%
  rename(b = Estimate, se = Std..Error, t = t.value, p = Pr...t..) %>%
  mutate_at(vars(b, se, t), funs(round2)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001",
                    format(round(p, 3), digits = 3)),
         param = factor(param,
                        levels = c("(Intercept)", 
                                   "ctryghana", 
                                   "ctrythailand",
                                   "ctrychina", 
                                   "ctryvanuatu", 
                                   "`VISQ: inner speech`",
                                   "`VISQ: inner speech`:ctryghana", 
                                   "`VISQ: inner speech`:ctrythailand", 
                                   "`VISQ: inner speech`:ctrychina", 
                                   "`VISQ: inner speech`:ctryvanuatu"),
                        labels = c("baserate (overall)", 
                                   "baserate (ghana vs. overall)",
                                   "baserate (thailand vs. overall)",
                                   "baserate (china vs. overall)",
                                   "baserate (vanuatu vs. overall)",
                                   "VISQ inner speech (overall)",
                                   "VISQ inner speech (ghana vs. overall)",
                                   "VISQ inner speech (thailand vs. overall)",
                                   "VISQ inner speech (china vs. overall)",
                                   "VISQ inner speech (vanuatu vs. overall)"))) %>%
  arrange(param) %>%
  column_to_rownames("param")

knitr::kable(r2_coef)
```

As above, these results indicate that there was a significant positive relationship between inner speech (as measured by the VISQ) and reported hallucination-like events, collapsing across sites ($b$ = `r r2_coef["VISQ inner speech (overall)", "b"]`, $p$ = `r r2_coef["VISQ inner speech (overall)", "p"]`). This test did not pick up on any substantial differences in the strength of this relationship across sites.

In the context of this test (i.e., controlling for these relationships), the differences across sites in overall baserates for reporting hallcunination-like events were not significant.

Here's a visualization of these relationships:

```{r, fig.width = 4, fig.asp = 0.375}
d_wide_subscale %>%
  filter(!is.na(`VISQ: inner speech`), !is.na(hallucination)) %>%
  ggplot(aes(x = `VISQ: inner speech`, # x = exwl_cent,
             y = hallucination, color = ctry)) +
  facet_grid(~ ctry) +
  geom_point(size = 1, alpha = 0.5) +
  geom_smooth(method = "lm", color = "black") +
  # geom_line(data = fortify(r1), aes(x = exwl_cent, y = .fitted), color = "black") +
  scale_color_brewer(palette = "Dark2") +
  scale_x_continuous(limits = c(-10, 10), breaks = seq(-100, 100, 2)) +
  scale_y_continuous(limits = c(0, 27), breaks = seq(-100, 100, 2)) +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(title = "Relationship between inner speech (VISQ) & hallucinations, by site",
       color = "Site",
       x = "Inner speech (VISQ; McCarthy-Jones & Fernyhough)",
       y = "Hallucinations (Alderson-Day)")
```

## ...as measured by the "dialogic speech" subscale of the VISQ

Here's a test for the overall correlation between dialogic speech as measured by the VISQ "dialogic speech" subscale, and hallucination-like experiences as measured by the Alderson-Day scale:

```{r}
cor3 <- with(d_wide_subscale, cor.test(`VISQ: dialogic speech`, hallucination)); cor3
```

Dialogic speech (as measured by VISQ) was significantly positively correlated with reported hallucination-like events ($r$ = `r round2(cor3$estimate)`, $p$ = `r ifelse(cor3$p.value < 0.001, "<0.001", format(round(cor3$p.value, 3), digits = 3))`), accounting for approximately `r round(cor3$estimate^2 * 100)`% of the variance in reported hallucinations.

Now let's take a look at what's going on in each site with a regression analysis:

```{r, results = "asis"}
r3 <- lm(hallucination ~ `VISQ: dialogic speech` * ctry, 
         d_wide_subscale %>% 
           mutate(`VISQ: dialogic speech` = scale(`VISQ: dialogic speech`, scale = F)))

r3_coef <- summary(r3)$coefficients %>%
  data.frame() %>%
  rownames_to_column("param") %>%
  rename(b = Estimate, se = Std..Error, t = t.value, p = Pr...t..) %>%
  mutate_at(vars(b, se, t), funs(round2)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001",
                    format(round(p, 3), digits = 3)),
         param = factor(param,
                        levels = c("(Intercept)", 
                                   "ctryghana", 
                                   "ctrythailand",
                                   "ctrychina", 
                                   "ctryvanuatu", 
                                   "`VISQ: dialogic speech`",
                                   "`VISQ: dialogic speech`:ctryghana", 
                                   "`VISQ: dialogic speech`:ctrythailand", 
                                   "`VISQ: dialogic speech`:ctrychina", 
                                   "`VISQ: dialogic speech`:ctryvanuatu"),
                        labels = c("baserate (overall)", 
                                   "baserate (ghana vs. overall)",
                                   "baserate (thailand vs. overall)",
                                   "baserate (china vs. overall)",
                                   "baserate (vanuatu vs. overall)",
                                   "VISQ dialogic speech (overall)",
                                   "VISQ dialogic speech (ghana vs. overall)",
                                   "VISQ dialogic speech (thailand vs. overall)",
                                   "VISQ dialogic speech (china vs. overall)",
                                   "VISQ dialogic speech (vanuatu vs. overall)"))) %>%
  arrange(param) %>%
  column_to_rownames("param")

knitr::kable(r3_coef)
```

These results indicate that there was a significant positive relationship between dialogic speech (as measured by the VISQ) and reported hallucination-like events, collapsing across sites ($b$ = `r r3_coef["VISQ dialogic speech (overall)", "b"]`, $p$ = `r r3_coef["VISQ dialogic speech (overall)", "p"]`). This test did not pick up on any substantial differences in the strength of this relationship across sites.

In the context of this test (i.e., controlling for these relationships), one of the differences across sites in the baserates for reporting hallucination-like events were again significant: Participants in Thailand generally reported fewer than average (Thailand: $b$ = `r r1_coef["baserate (thailand vs. overall)", "b"]`, $p$ = `r r1_coef["baserate (thailand vs. overall)", "p"]`).

Here's a visualization of these relationships:

```{r, fig.width = 4, fig.asp = 0.375}
d_wide_subscale %>%
  filter(!is.na(`VISQ: dialogic speech`), !is.na(hallucination)) %>%
  ggplot(aes(x = `VISQ: dialogic speech`, # x = exwl_cent,
             y = hallucination, color = ctry)) +
  facet_grid(~ ctry) +
  geom_point(size = 1, alpha = 0.5) +
  geom_smooth(method = "lm", color = "black") +
  # geom_line(data = fortify(r1), aes(x = exwl_cent, y = .fitted), color = "black") +
  scale_color_brewer(palette = "Dark2") +
  scale_x_continuous(limits = c(-8, 8), breaks = seq(-100, 100, 2)) +
  scale_y_continuous(limits = c(0, 27), breaks = seq(-100, 100, 2)) +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(title = "Relationship between dialogic speech (VISQ) & hallucinations, by site",
       color = "Site",
       x = "Dialogic speech (VISQ; McCarthy-Jones & Fernyhough)",
       y = "Hallucinations (Alderson-Day)")
```

## ...as measured by the "evaluative speech" subscale of the VISQ

Here's a test for the overall correlation between evaluative as measured by the VISQ "evaluative/motivational speech" subscale, and hallucination-like experiences as measured by the Alderson-Day scale:

```{r}
cor4 <- with(d_wide_subscale, cor.test(`VISQ: evaluative`, hallucination)); cor4
```

Evaluative/motivational speech (as measured by VISQ) was significantly positively correlated with reported hallucination-like events ($r$ = `r round2(cor4$estimate)`, $p$ = `r ifelse(cor4$p.value < 0.001, "<0.001", format(round(cor4$p.value, 3), digits = 3))`), accounting for approximately `r round(cor4$estimate^2 * 100)`% of the variance in reported hallucinations.

Now let's take a look at what's going on in each site with a regression analysis:

```{r, results = "asis"}
r4 <- lm(hallucination ~ `VISQ: evaluative` * ctry, 
         d_wide_subscale %>% 
           mutate(`VISQ: evaluative` = scale(`VISQ: evaluative`, scale = F)))

r4_coef <- summary(r4)$coefficients %>%
  data.frame() %>%
  rownames_to_column("param") %>%
  rename(b = Estimate, se = Std..Error, t = t.value, p = Pr...t..) %>%
  mutate_at(vars(b, se, t), funs(round2)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001",
                    format(round(p, 3), digits = 3)),
         param = factor(param,
                        levels = c("(Intercept)", 
                                   "ctryghana", 
                                   "ctrythailand",
                                   "ctrychina", 
                                   "ctryvanuatu", 
                                   "`VISQ: evaluative`",
                                   "`VISQ: evaluative`:ctryghana", 
                                   "`VISQ: evaluative`:ctrythailand", 
                                   "`VISQ: evaluative`:ctrychina", 
                                   "`VISQ: evaluative`:ctryvanuatu"),
                        labels = c("baserate (overall)", 
                                   "baserate (ghana vs. overall)",
                                   "baserate (thailand vs. overall)",
                                   "baserate (china vs. overall)",
                                   "baserate (vanuatu vs. overall)",
                                   "VISQ eval/motiv (overall)",
                                   "VISQ eval/motiv (ghana vs. overall)",
                                   "VISQ eval/motiv (thailand vs. overall)",
                                   "VISQ eval/motiv (china vs. overall)",
                                   "VISQ eval/motiv (vanuatu vs. overall)"))) %>%
  arrange(param) %>%
  column_to_rownames("param")

knitr::kable(r4_coef)
```

These results indicate that there was a significant positive relationship between evaluative/motivational speech (as measured by the VISQ) and reported hallucination-like events, collapsing across sites ($b$ = `r r4_coef["VISQ evaluative (overall)", "b"]`, $p$ = `r r4_coef["VISQ evaluative (overall)", "p"]`). This test did not pick up on any substantial differences in the strength of this relationship across sites.

In the context of this test (i.e., controlling for these relationships), a few differences across sites in the baserates for reporting hallucination-like events were again significant: Yet again, participants in Thailand generally reported fewer than average, as did participants in China (Thailand: $b$ = `r r1_coef["baserate (thailand vs. overall)", "b"]`, $p$ = `r r1_coef["baserate (thailand vs. overall)", "p"]`; China: $b$ = `r r1_coef["baserate (china vs. overall)", "b"]`, $p$ = `r r1_coef["baserate (china vs. overall)", "p"]`).

Here's a visualization of these relationships:

```{r, fig.width = 4, fig.asp = 0.375}
d_wide_subscale %>%
  filter(!is.na(`VISQ: evaluative`), !is.na(hallucination)) %>%
  ggplot(aes(x = `VISQ: evaluative`, # x = exwl_cent,
             y = hallucination, color = ctry)) +
  facet_grid(~ ctry) +
  geom_point(size = 1, alpha = 0.5) +
  geom_smooth(method = "lm", color = "black") +
  # geom_line(data = fortify(r1), aes(x = exwl_cent, y = .fitted), color = "black") +
  scale_color_brewer(palette = "Dark2") +
  scale_x_continuous(limits = c(-8, 8), breaks = seq(-100, 100, 2)) +
  scale_y_continuous(limits = c(0, 27), breaks = seq(-100, 100, 2)) +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(title = "Relationship between evaluative/motivational speech (VISQ) & hallucinations, by site",
       color = "Site",
       x = "Evaluative/motivational speech (VISQ; McCarthy-Jones & Fernyhough)",
       y = "Hallucinations (Alderson-Day)")
```

