---
title: 'Grappling with the "Daily Spiritual Experiences" scale'
subtitle: 'Last updated 2018-04-07'
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r, include = FALSE}
# set working director
# setwd("/Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_packets/packets123/")

# load packages
library(tidyverse)
library(rms)
library(ggdendro)
library(psych)

# load question key (including manual reverse-coding)
question_key <- read.csv("//Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_packets/packets123/packets123_question_key_byhand.csv")

# load data (reverse-coded)
d_long <- read_csv("//Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_packets/packets123/packets123_data_byquestion_long.csv") %>%
  mutate(ctry = factor(ctry, 
                       levels = c("us", "ghana", "thailand", "china", "vanuatu")))
d_long_subscale <- read_csv("//Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_packets/packets123/packets123_data_bysubscale_long.csv") %>%
  mutate(ctry = factor(ctry, 
                       levels = c("us", "ghana", "thailand", "china", "vanuatu")))

# load data (before reverse-coding)
d_all <- read.csv("//Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_packets/packets123/packets123_data.csv")

# make custom functions
round2 <- function(x) {format(round(x, 2), digits = 2)}
```

Here we look at the "daily spiritual experiences" scale (Underwood & Teresi; Packet 1) in detail.

**NOTE**: There were four on this scale (`dse_07`, `dse_08`, `dse_15`, and `dse_16`), where Thai participants answered a bunch of different questions instead of just one (these were questions dealing with multiple spiritual entities instead of just "God"). Here, we deal with this by "crediting" Thai participants with their *maximum* response for *any* of the options for that question (i.e., if they answered at the extreme negative end of the response scale for all but one question, and at the extreme positive end for one question, they'd get "credited" with the extreme positive response). For our current purposes, I have *not* kept track of which particular question this was.

# Differences across fieldsites

## Mean scores by site

First, let's look at scores for Questions #1-14 for participants in each site (Tanya indicated that this was a separate subscale):

```{r, include = F}
d_long_subscale_boot <- d_long_subscale %>%
  filter(!is.na(sum_score)) %>%
  group_by(ctry, packet, subscale) %>%
  do(data.frame(rbind(smean.cl.boot(.$sum_score)))) %>%
  ungroup() %>%
  filter(subscale != "attn") %>%
  left_join(d_long_subscale %>%
              filter(!is.na(sum_score)) %>%
              count(ctry, packet, subscale)) %>%
  mutate(packet = paste("packet", packet),
         ctry = factor(ctry,
                       levels = c("us", "ghana", 
                                  "thailand", "china", "vanuatu")),
         subscale = 
           factor(subscale,
                  levels = c("exwl", 
                             "exwl_extra",
                             "dse_01to14", 
                             "dse_15to16", 
                             "spev", 
                             "sen_sensory_seeking", 
                             "sen_body_awareness", 
                             "sen_trait_metamood",
                             "her2_hallucination",
                             "invo_VISQ_dialogic_speech", 
                             "invo_VISQ_inner_speech",
                             "invo_VISQ_eval_motiv_inner_speech",
                             "invo_hardy_bentall",
                             "her_posey_losch",
                             "enco_lewicki",
                             "meta_van_elk",
                             "tat_confidence",
                             "tat_positive_beliefs",
                             "tat_cognitive",
                             "tat_uncontrollability",
                             "tat_need_control",
                             "minw_mental_states",
                             "minw_life_events",
                             "minw_inanimate",
                             "minw_selves_souls_world",
                             "minw_epistemic"),
                  labels = c("absorption (tellegen)", 
                             "absorption (extra)",
                             "daily spiritual experiences (#1-14)",
                             "daily spiritual experiences (#15-16)",
                             "spiritual events", 
                             "sensory seeking",
                             "body awareness", 
                             "attention to feelings",
                             "hallucination", 
                             "VISQ: dialogic speech",
                             "VISQ: inner speech",
                             "VISQ: evaluative",
                             "inner speech",
                             "hearing events",
                             "encoding style",
                             "mind metaphors",
                             "metacog.: lack of cognitive confidence",
                             "metacog.: positive beliefs re: worrying",
                             "metacog.: cognitive self-consciousness",
                             "metacog.: uncontrollability/danger",
                             "metacog.: need to control thoughts",
                             "dualism: mental states",
                             "dualism: life events",
                             "dualism: inanimate consciousness",
                             "dualism: minds, selves, & world",
                             "dualism: epistemology")))
```

```{r, fig.width = 3, fig.asp = 0.9}
ggplot(d_long_subscale_boot %>%
         filter(subscale == "daily spiritual experiences (#1-14)"),
       aes(x = ctry, y = Mean)) +
  # geom_hline(aes(yintercept = 0), lty = 2, color = "black") +
  # geom_hline(aes(yintercept = 36), lty = 2, color = "black") +
  geom_point(data = d_long_subscale %>%
               filter(subscale == "dse_01to14",
                      !is.na(sum_score)),
             aes(y = sum_score, color = ctry),
             position = position_jitter(width = 0.3, height = 0),
             alpha = 0.3, size = 1) +
  geom_pointrange(aes(ymin = Lower, ymax = Upper)) +
  geom_text(aes(label = paste0("(n=", n, ")"), y = Lower), 
            size = 2, nudge_x = 0.15, hjust = 0) +
  # scale_x_discrete(expand = c(0, 1)) +
  scale_y_continuous(limits = c(-0.5, 70.5), breaks = seq(0, 100, 10)) +
  scale_color_brewer(palette = "Dark2") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none") +
  labs(title = "Mean daily spiritual experiences scores (#1-14) by site\n(Underwood & Teresi)",
       subtitle = "A higher score indicates more endorsements of 'spiritual' experiences (range: 0-70)\nError bars are bootstrapped 95% confidence intervals",
       x = "Site", color = "Site",
       y = "Mean score")
```

Note that this plot includes both average scores for each site (in black), and individual scores for all of the participants in that site (small, colorful points in the background, which are "jittered" around a little so that you can see them all).

Looks like people in different sites responded quite differently to this scale! As with the "spiritual events" scale (Luhrmann; see other doc), participants in Ghana and Vanuatu responded much more positively; participants in the US and Thailand look about the same to me, and participants in China here seem to have responded substantially more negatively. 

Let's also look at the "extra" items about closeness to God* (questions #15-16), in the aggregate:

```{r, fig.width = 3, fig.asp = 0.9}
ggplot(d_long_subscale_boot %>%
         filter(subscale == "daily spiritual experiences (#15-16)"),
       aes(x = ctry, y = Mean)) +
  # geom_hline(aes(yintercept = 0), lty = 2, color = "black") +
  # geom_hline(aes(yintercept = 4), lty = 2, color = "black") +
  geom_point(data = d_long_subscale %>%
               filter(subscale == "dse_15to16",
                      !is.na(sum_score)),
             aes(y = sum_score, color = ctry),
             position = position_jitter(width = 0.3, height = 0.15),
             alpha = 0.3, size = 1) +
  geom_pointrange(aes(ymin = Lower, ymax = Upper)) +
  geom_text(aes(label = paste0("(n=", n, ")"), y = Lower), 
            size = 2, nudge_x = 0.15, hjust = 0) +
  # scale_x_discrete(expand = c(0, 1)) +
  scale_y_continuous(limits = c(-0.5, 10.5), breaks = seq(0, 100, 2)) +
  scale_color_brewer(palette = "Dark2") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none") +
  labs(title = "Mean daily spiritual experiences scores (#15-16) by site\n(Underwood & Teresi)",
       subtitle = "A higher score indicates more endorsements of 'close to God' items (range: 0-10)\nError bars are bootstrapped 95% confidence intervals",
       x = "Site", color = "Site",
       y = "Mean score")
```

Again, this plot includes both average scores for each site (in black), and individual scores for all of the participants in that site (small, colorful points in the background, which are "jittered" around a little so that you can see them all).

Very similar pattern to what we saw above. 

Now let's look at these differences in more detail using the "raw data" for individual questions, rather than these subscale scores.

## Responses by question, by site

```{r, fig.width = 10, fig.asp = 0.7}
d_plot <- d_long %>%
  filter(grepl("dse_", question), !grepl("attn", question)) %>%
  left_join(question_key %>%
              distinct(question_label_universal, 
                       question_text,
                       byhand_coding,
                       byhand_subscale) %>%
              rename(question = question_label_universal,
                     coding = byhand_coding,
                     subscale = byhand_subscale)) %>%
  distinct() %>%
  mutate(coding = factor(coding,
                         levels = c("-1", "1"),
                         labels = c("(REVERSED)", "")),
         question_text_short = gsub('(.{1,30})(\\s|$)',
                                    '\\1\n',
                                    paste0(question,
                                           ": ",
                                           substr(question_text,
                                                  start = 1, stop = 10000),
                                           # "...",
                                           coding))) %>%
  count(ctry, subscale, question_text_short, response) %>%
  spread(response, n) %>%
  mutate_at(vars(`0`:`5`), 
            funs(replace(., is.na(.), 0))) %>%
  arrange(ctry, `0`) %>%
  rownames_to_column("order") %>%
  mutate(order = as.numeric(order),
         nonzero_n = `1` + `2` + `3` + `4` + `5`,
         total_n = `0` + `1` + `2` + `3` + `4` + `5`) %>%
  gather(response, n, c(`0`, `1`, `2`, `3`, `4`, `5`)) %>%
  mutate(response = factor(response,
                           levels = c("0", "1", "2", "3", "4", "5")),
         ctry = factor(ctry,
                       levels = c("us", "ghana", "thailand", 
                                  "china", "vanuatu"),
                       labels = c("US", "Ghana", "Thailand", 
                                  "China", "Vanuatu"))) %>%
  distinct()

adjust <- 15
custom_palette <- c("#f6eff7", "#d0d1e6", "#a6bddb", 
                    "#67a9cf", "#1c9099", "#016c59",
                    "#feebe2", "#fbb4b9", "#f768a1", "#ae017e")

ggplot(d_plot %>%
         mutate(response_text = factor(case_when(
           subscale == "dse_01to14" ~ case_when(
             response == "0" ~ "Never",
             response == "1" ~ "Once in a while",
             response == "2" ~ "Some days",
             response == "3" ~ "Most days",
             response == "4" ~ "Every day",
             response == "5" ~ "Many times a day"),
           subscale == "dse_15to16" ~ case_when(
             response == "0" ~ "Not at all close",
             response == "1" ~ "Somewhat close",
             response == "2" ~ "Very close",
             response == "3" ~ "As close as possible")),
           levels = c("Never", "Once in a while", "Some days", "Most days",
                      "Every day", "Many times a day", "Not at all close", 
                      "Somewhat close", "Very close", "As close as possible"))) %>%
         filter(!is.na(response_text)),
       aes(x = reorder(question_text_short, desc(question_text_short)),
           # x = reorder(question_text_short, desc(order)),
           y = n, fill = response_text)) +
  facet_grid(factor(subscale,
                    levels = c("dse_01to14", "dse_15to16"),
                    labels = c("Questions #1-14", "Closeness to God*")) ~ ctry, 
             scales = "free", space = "free") +
  geom_bar(position = position_stack(), stat = "identity", 
           color = "black", size = 0.2) +
  geom_text(data = d_plot %>% 
              distinct(ctry, subscale, question_text_short, order, 
                       nonzero_n, total_n),
            aes(y = max(d_plot$total_n) + adjust, fill = NULL,
                label = paste0(round(nonzero_n/total_n, 2)*100, "%")), 
            size = 3, hjust = 1) +
  scale_y_continuous(limits = c(0, max(d_plot$total_n) + adjust)) +
  scale_fill_manual(values = custom_palette) +
  theme_bw() +
  labs(title = "Responses to 'Daily spiritual experiences' (Underwood & Teresi) scale items",
       subtitle = "'*' denotes a question where 'God' was replaced by a variety of different beings for Thai participants (questions #7, 8, 15, & 16); the participants' highest response has been retained here\n% corresponds to a response more than 'Never' (darker colors)",
       x = "", y = "Count of responses", fill = "Response") +
  theme(legend.position = "top",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  # theme(axis.text.x = element_text(angle = 90, hjust = 1))
  guides(fill = guide_legend(ncol = 6, byrow = TRUE)) +
  coord_flip()

rm(adjust)
```

VERY eager to hear others' observations... lots to chew on here. Off the top of my head, a few things stand out:

- Tons of positive responses in GH and VT, to almost every item. Troubling? Interesting? Both?
- Tons of negative responses in CH. Troubling? Interesting? Both?
- People may have used the response scale differently in different places (attention **Emily**, who raised this question!): e.g., people in CH almost never used the "Every day" or "Many times a day" extreme responses, while people GH and VT almost never used the "Never" extreme response.

This is just the tip of the iceberg. Tons to think through here.

# Distribution of responses for individual participants, by site

Another thing we might be interested in is how individual participants responded: Were there people who said yes to everything, or no to everything? How do these distributions of responses differ across participants in different sites?

Let's take a look:

```{r, fig.width = 6, fig.asp = 1}
d_long %>%
  filter(grepl("dse_", question),
         !grepl("attn", question),
         !is.na(response)) %>%
  left_join(question_key %>%
              distinct(question_label_universal, 
                       question_text,
                       byhand_coding,
                       byhand_subscale) %>%
              rename(question = question_label_universal,
                     coding = byhand_coding,
                     subscale = byhand_subscale)) %>%
  distinct() %>%
  mutate(response = factor(response),
         coding = factor(coding,
                         levels = c("-1", "1"),
                         labels = c("(REVERSED)", "")),
         question_text_short = gsub('(.{1,130})(\\s|$)',
                                    '\\1\n',
                                    paste0(substr(question_text,
                                                     start = 1, stop = 10000),
                                              # "...",
                                              coding)),
         subscale = factor(subscale, 
                           levels = c("dse_01to14", "dse_15to16"),
                           labels = c("Daily spiritual experiences #1-14 (Underwood & Teresi)", "Closeness to God* (Underwood & Teresi)"))) %>%
  filter(subscale == "Daily spiritual experiences #1-14 (Underwood & Teresi)") %>%
  distinct() %>%
  count(ctry, subscale, subj, response) %>%
  spread(response, n) %>%
  mutate_at(vars(c(`0`, `1`, `2`, `3`, `4`, `5`)), funs(replace(., is.na(.), 0))) %>%
  mutate(total_n = `0` + `1` + `2` + `3` + `4` + `5`,
         prop_0 = `0`/total_n,
         prop_1 = `1`/total_n,
         prop_2 = `2`/total_n,
         prop_3 = `3`/total_n,
         prop_4 = `4`/total_n,
         prop_5 = `5`/total_n,
         ctry = factor(ctry,
                       levels = c("us", "ghana", "thailand", 
                                  "china", "vanuatu"),
                       labels = c("US", "Ghana", "Thailand", 
                                  "China", "Vanuatu"))) %>%
  distinct() %>%
  select(-c(`0`, `1`, `2`, `3`, `4`, `5`)) %>%
  gather(response, prop, starts_with("prop")) %>%
  mutate(response = factor(response,
                           labels = c("Never", "Once in a while", "Some days",
                                      "Most days", "Every day", 
                                      "Many times a day"))) %>%
  distinct() %>%
  ggplot(aes(x = prop, fill = ctry)) +
  facet_grid(response ~ ctry, scales = "free", space = "free") +
  geom_histogram(binwidth = 1/14) +
  scale_x_continuous(breaks = seq(0, 1, 0.25)) +
  scale_y_continuous(breaks = seq(0, 1000, 10)) +
  scale_fill_brewer(palette = "Dark2") +
  theme_bw() +
  labs(title = "Distributions of how many times participants endorsed each response option\nfor the 'Daily spiritual experiences' (Underwood & Teresi) scale items #1-14",
       x = "Proportion of responses (at the individual participant level)", y = "Count of participants", fill = "Site") +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))
```

```{r, fig.width = 6, fig.asp = 0.7}
d_long %>%
  filter(grepl("dse_", question),
         !grepl("attn", question),
         !is.na(response)) %>%
  left_join(question_key %>%
              distinct(question_label_universal, 
                       question_text,
                       byhand_coding,
                       byhand_subscale) %>%
              rename(question = question_label_universal,
                     coding = byhand_coding,
                     subscale = byhand_subscale)) %>%
  distinct() %>%
  mutate(response = factor(response),
         coding = factor(coding,
                         levels = c("-1", "1"),
                         labels = c("(REVERSED)", "")),
         question_text_short = gsub('(.{1,130})(\\s|$)',
                                    '\\1\n',
                                    paste0(substr(question_text,
                                                     start = 1, stop = 10000),
                                              # "...",
                                              coding)),
         subscale = factor(subscale, 
                           levels = c("dse_01to14", "dse_15to16"),
                           labels = c("Daily spiritual experiences #1-14 (Underwood & Teresi)", "Closeness to God* (Underwood & Teresi)"))) %>%
  filter(subscale == "Closeness to God* (Underwood & Teresi)") %>%
  distinct() %>%
  count(ctry, subscale, subj, response) %>%
  spread(response, n) %>%
  mutate_at(vars(c(`0`, `1`, `2`, `3`)), funs(replace(., is.na(.), 0))) %>%
  mutate(total_n = `0` + `1` + `2` + `3`,
         prop_0 = `0`/total_n,
         prop_1 = `1`/total_n,
         prop_2 = `2`/total_n,
         prop_3 = `3`/total_n,
         ctry = factor(ctry,
                       levels = c("us", "ghana", "thailand", 
                                  "china", "vanuatu"),
                       labels = c("US", "Ghana", "Thailand", 
                                  "China", "Vanuatu"))) %>%
  distinct() %>%
  select(-c(`0`, `1`, `2`, `3`)) %>%
  gather(response, prop, starts_with("prop")) %>%
  mutate(response = factor(response,
                           labels = c("Not at all close", "Somewhat close",
                                      "Very close", "As close as possible"))) %>%
  distinct() %>%
  ggplot(aes(x = prop, fill = ctry)) +
  facet_grid(response ~ ctry, scales = "free", space = "free") +
  geom_histogram(binwidth = 1/2) +
  scale_x_continuous(breaks = seq(0, 1, 0.5)) +
  scale_y_continuous(breaks = seq(0, 1000, 10)) +
  scale_fill_brewer(palette = "Dark2") +
  theme_bw() +
  labs(title = "Distributions of how many times participants endorsed each response option\nfor the 'Closeness to God*' (Underwood & Teresi) scale items #15-16",
       x = "Proportion of responses (at the individual participant level)", y = "Count of participants", fill = "Site") +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))
```

Again, lots to chew on here, and I haven't taken a close look at any of this.

Just for fun, here's another way to look at the same data, overlaying the density distributions for each site on top of each other to see where they seem to be similar/different:

```{r, fig.width = 3, fig.asp = 3}
d_long %>%
  filter(grepl("dse_", question),
         !grepl("attn", question),
         !is.na(response)) %>%
  left_join(question_key %>%
              distinct(question_label_universal, 
                       question_text,
                       byhand_coding,
                       byhand_subscale) %>%
              rename(question = question_label_universal,
                     coding = byhand_coding,
                     subscale = byhand_subscale)) %>%
  filter(subscale == "dse_01to14") %>%
  distinct() %>%
  mutate(coding = factor(coding,
                         levels = c("-1", "1"),
                         labels = c("(REVERSED)", "")),
         question_text_short = gsub('(.{1,130})(\\s|$)',
                                    '\\1\n',
                                    paste0(substr(question_text,
                                                     start = 1, stop = 10000),
                                              # "...",
                                              coding)),
         subscale = factor(subscale, 
                           levels = c("dse_01to14"),
                           labels = c("Daily spiritual experiences (Underwood & Teresi)"))) %>%
  distinct() %>%
  count(ctry, subscale, subj, response) %>%
  spread(response, n) %>%
  mutate_at(vars(c(`0`, `1`, `2`, `3`, `4`, `5`)), funs(replace(., is.na(.), 0))) %>%
  mutate(total_n = `0` + `1` + `2` + `3` + `4` + `5`,
         prop_0 = `0`/total_n,
         prop_1 = `1`/total_n,
         prop_2 = `2`/total_n,
         prop_3 = `3`/total_n,
         prop_4 = `4`/total_n,
         prop_5 = `5`/total_n,
         ctry = factor(ctry,
                       levels = c("us", "ghana", "thailand", 
                                  "china", "vanuatu"),
                       labels = c("US", "Ghana", "Thailand", 
                                  "China", "Vanuatu"))) %>%
  distinct() %>%
  select(-c(`0`, `1`, `2`, `3`, `4`, `5`)) %>%
  gather(response, prop, starts_with("prop")) %>%
  mutate(response = factor(response,
                           labels = c("Never", "Once in a while", "Some days",
                                      "Most days", "Every day", 
                                      "Many times a day"))) %>%
  ggplot(aes(x = prop, fill = ctry)) +
  facet_grid(response ~ ., scales = "free", space = "fixed") +
  geom_density(alpha = 0.3) +
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.25)) +
  scale_fill_brewer(palette = "Dark2") +
  theme_bw() +
  labs(title = "Distributions of how many times participants endorsed each\nresponse option for the 'Daily spiritual experiences'\n(Underwood & Teresi) scale items #1-14",
       x = "Proportion of responses (at the individual participant level)", y = "Count of participants", fill = "Site") +
  theme(legend.position = "top",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))
```

```{r, fig.width = 3, fig.asp = 2}
d_long %>%
  filter(grepl("dse_", question),
         !grepl("attn", question),
         !is.na(response)) %>%
  left_join(question_key %>%
              distinct(question_label_universal, 
                       question_text,
                       byhand_coding,
                       byhand_subscale) %>%
              rename(question = question_label_universal,
                     coding = byhand_coding,
                     subscale = byhand_subscale)) %>%
  filter(subscale == "dse_15to16") %>%
  distinct() %>%
  mutate(coding = factor(coding,
                         levels = c("-1", "1"),
                         labels = c("(REVERSED)", "")),
         question_text_short = gsub('(.{1,130})(\\s|$)',
                                    '\\1\n',
                                    paste0(substr(question_text,
                                                     start = 1, stop = 10000),
                                              # "...",
                                              coding)),
         subscale = factor(subscale, 
                           levels = c("dse_15to16"),
                           labels = c("Closeness to God* (Underwood & Teresi)"))) %>%
  distinct() %>%
  count(ctry, subscale, subj, response) %>%
  spread(response, n) %>%
  mutate_at(vars(c(`0`, `1`, `2`, `3`)), funs(replace(., is.na(.), 0))) %>%
  mutate(total_n = `0` + `1` + `2` + `3`,
         prop_0 = `0`/total_n,
         prop_1 = `1`/total_n,
         prop_2 = `2`/total_n,
         prop_3 = `3`/total_n,
         ctry = factor(ctry,
                       levels = c("us", "ghana", "thailand", 
                                  "china", "vanuatu"),
                       labels = c("US", "Ghana", "Thailand", 
                                  "China", "Vanuatu"))) %>%
  distinct() %>%
  select(-c(`0`, `1`, `2`, `3`)) %>%
  gather(response, prop, starts_with("prop")) %>%
  mutate(response = factor(response,
                           labels = c("Not at all close", "Somewhat close",
                                      "Very close", "As close as possible"))) %>%
  ggplot(aes(x = prop, fill = ctry)) +
  facet_grid(response ~ ., scales = "free", space = "fixed") +
  geom_density(alpha = 0.3) +
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.5)) +
  scale_fill_brewer(palette = "Dark2") +
  theme_bw() +
  labs(title = "Distributions of how many times participants endorsed each\nresponse option for the 'Closeness to God*'\n(Underwood & Teresi) scale items #15-16",
       x = "Proportion of responses (at the individual participant level)", y = "Count of participants", fill = "Site") +
  theme(legend.position = "top",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))
```
