---
title: 'Grappling with the "Sensory seeking" scale'
subtitle: 'Last updated 2018-04-07'
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r, include = FALSE}
# set working director
# setwd("/Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_packets/packets123/")

# load packages
library(tidyverse)
library(rms)
library(ggdendro)
library(psych)

# load question key (including manual reverse-coding)
question_key <- read.csv("//Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_packets/packets123/packets123_question_key_byhand.csv")

# load data (reverse-coded)
d_long <- read_csv("//Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_packets/packets123/packets123_data_byquestion_long.csv") %>%
  mutate(ctry = factor(ctry, 
                       levels = c("us", "ghana", "thailand", "china", "vanuatu")))
d_long_subscale <- read_csv("//Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_packets/packets123/packets123_data_bysubscale_long.csv") %>%
  mutate(ctry = factor(ctry, 
                       levels = c("us", "ghana", "thailand", "china", "vanuatu")))

# load data (before reverse-coding)
d_all <- read.csv("//Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_packets/packets123/packets123_data.csv")

# make custom functions
round2 <- function(x) {format(round(x, 2), digits = 2)}
```

Here we look at the "sensory seeking" scale (Brown et al.; Packet 2) in detail.

# Differences across fieldsites

## Mean scores by site

First, let's look at scores for participants in each site:

```{r, include = F}
d_long_subscale_boot <- d_long_subscale %>%
  filter(!is.na(sum_score)) %>%
  group_by(ctry, packet, subscale) %>%
  do(data.frame(rbind(smean.cl.boot(.$sum_score)))) %>%
  ungroup() %>%
  filter(subscale != "attn") %>%
  left_join(d_long_subscale %>%
              filter(!is.na(sum_score)) %>%
              count(ctry, packet, subscale)) %>%
  mutate(packet = paste("packet", packet),
         ctry = factor(ctry,
                       levels = c("us", "ghana", 
                                  "thailand", "china", "vanuatu")),
         subscale = 
           factor(subscale,
                  levels = c("exwl", 
                             "exwl_extra",
                             "dse_01to14", 
                             "dse_15to16", 
                             "spev", 
                             "sen_sensory_seeking", 
                             "sen_body_awareness", 
                             "sen_trait_metamood",
                             "her2_hallucination",
                             "invo_VISQ_dialogic_speech", 
                             "invo_VISQ_inner_speech",
                             "invo_VISQ_eval_motiv_inner_speech",
                             "invo_hardy_bentall",
                             "her_posey_losch",
                             "enco_lewicki",
                             "meta_van_elk",
                             "tat_confidence",
                             "tat_positive_beliefs",
                             "tat_cognitive",
                             "tat_uncontrollability",
                             "tat_need_control",
                             "minw_mental_states",
                             "minw_life_events",
                             "minw_inanimate",
                             "minw_selves_souls_world",
                             "minw_epistemic"),
                  labels = c("absorption (tellegen)", 
                             "absorption (extra)",
                             "daily spiritual experiences (#1-14)",
                             "daily spiritual experiences (#15-16)",
                             "spiritual events", 
                             "sensory seeking",
                             "body awareness", 
                             "attention to feelings",
                             "hallucination", 
                             "VISQ: dialogic speech",
                             "VISQ: inner speech",
                             "VISQ: evaluative",
                             "inner speech",
                             "hearing events",
                             "encoding style",
                             "mind metaphors",
                             "metacog.: lack of cognitive confidence",
                             "metacog.: positive beliefs re: worrying",
                             "metacog.: cognitive self-consciousness",
                             "metacog.: uncontrollability/danger",
                             "metacog.: need to control thoughts",
                             "dualism: mental states",
                             "dualism: life events",
                             "dualism: inanimate consciousness",
                             "dualism: minds, selves, & world",
                             "dualism: epistemology")))
```

```{r, fig.width = 3, fig.asp = 0.9}
ggplot(d_long_subscale_boot %>%
         filter(subscale == "sensory seeking"),
       aes(x = ctry, y = Mean)) +
  # geom_hline(aes(yintercept = 0), lty = 2, color = "black") +
  # geom_hline(aes(yintercept = 36), lty = 2, color = "black") +
  geom_point(data = d_long_subscale %>%
               filter(subscale == "sen_sensory_seeking",
                      !is.na(sum_score)),
             aes(y = sum_score, color = ctry),
             position = position_jitter(width = 0.3, height = 0),
             alpha = 0.3, size = 1) +
  geom_pointrange(aes(ymin = Lower, ymax = Upper)) +
  geom_text(aes(label = paste0("(n=", n, ")"), y = Lower), 
            size = 2, nudge_x = 0.15, hjust = 0) +
  # scale_x_discrete(expand = c(0, 1)) +
  scale_y_continuous(limits = c(-28.5, 28.5), breaks = seq(-100, 100, 10)) +
  scale_color_brewer(palette = "Dark2") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none") +
  labs(title = "Mean sensory seeking scores by site (Brown et al.)",
       subtitle = "A higher score indicates more endorsements of 'sensory seeking' (range: -28 to 28)\nError bars are bootstrapped 95% confidence intervals",
       x = "Site", color = "Site",
       y = "Mean score")
```

Note that this plot includes both average scores for each site (in black), and individual scores for all of the participants in that site (small, colorful points in the background, which are "jittered" around a little so that you can see them all).

Looks like people in different sites responded somewhat differently to this scale! Participants in the US and Vanuatu responded somewhat more positively; participants in Thailand and China somewhat more neutrally/negatively. 

Now let's look at these differences in more detail using the "raw data" for individual questions, rather than these subscale scores.

## Responses by question, by site

```{r, fig.width = 10, fig.asp = 0.6}
d_plot <- d_long %>%
  filter(question %in% c("sen_01", "sen_02", "sen_03", "sen_04", "sen_05",
                         "sen_06", "sen_07", "sen_08", "sen_09", "sen_10",
                         "sen_11", "sen_12", "sen_13", "sen_14"),
         !grepl("attn", question)) %>%
  left_join(question_key %>%
              distinct(question_label_universal, 
                       question_text,
                       byhand_coding,
                       byhand_subscale) %>%
              rename(question = question_label_universal,
                     coding = byhand_coding,
                     subscale = byhand_subscale)) %>%
  distinct() %>%
  mutate(coding = factor(coding,
                         levels = c("-1", "1"),
                         labels = c("(REVERSED)", "")),
         question_text_short = gsub('(.{1,30})(\\s|$)',
                                    '\\1\n',
                                    paste0(question,
                                           ": ",
                                           substr(question_text,
                                                  start = 1, stop = 10000),
                                           # "...",
                                           coding))) %>%
  count(ctry, question_text_short, response) %>%
  spread(response, n) %>%
  mutate_at(vars(`-2`:`2`), 
            funs(replace(., is.na(.), 0))) %>%
  arrange(ctry, `-2`) %>%
  rownames_to_column("order") %>%
  mutate(order = as.numeric(order),
         agree_n = `1` + `2`,
         total_n = `-2` + `-1` + `0` + `1` + `2`) %>%
  gather(response, n, c(`-2`, `-1`, `0`, `1`, `2`)) %>%
  mutate(response = factor(response,
                           levels = c("-2", "-1", "0", "1", "2")),
         ctry = factor(ctry,
                       levels = c("us", "ghana", "thailand", 
                                  "china", "vanuatu"),
                       labels = c("US", "Ghana", "Thailand", 
                                  "China", "Vanuatu"))) %>%
  distinct()

adjust <- 15

ggplot(d_plot %>%
         mutate(response = factor(response,
                                  labels = c("Strongly disagree", "Disagree", 
                                             "Neither agree nor disagree",
                                             "Agree", "Strongly agree"))),
       aes(x = reorder(question_text_short, desc(question_text_short)),
           # x = reorder(question_text_short, desc(order)),
           y = n, fill = response)) +
  facet_grid(. ~ ctry, scales = "free", space = "free") +
  geom_bar(position = position_stack(), stat = "identity", 
           color = "black", size = 0.2) +
  geom_text(data = d_plot %>% 
              distinct(ctry, question_text_short, order, 
                       agree_n, total_n),
            aes(y = max(d_plot$total_n) + adjust, fill = NULL,
                label = paste0(round(agree_n/total_n, 2)*100, "%")), 
            size = 3, hjust = 1) +
  scale_y_continuous(limits = c(0, max(d_plot$total_n) + adjust)) +
  scale_fill_brewer(palette = "PRGn") +
  theme_bw() +
  labs(title = "Responses to 'Sensory seeking' (Brown et al.) scale items",
       subtitle = "% corresponds to responses of 'Agree' or 'Strongly agree' (green)",
       x = "", y = "Count of responses", fill = "Response") +
  theme(legend.position = "top",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  # theme(axis.text.x = element_text(angle = 90, hjust = 1))
  coord_flip()

rm(adjust)
```

As always, lots to chew on here. Off the top of my head, a few things stand out:

- More use of the neutral midpoint in TH and CH, as we anticipated in informal discussions.
- At a glance, it seems like plenty of people in VT were using the "disagree" end of the scale (purple)... though let's also look at this at an individual level (below).
- People in CH really tended to agree that they "like to do things on the spur of the moment"! (`sen_04`)
- People in the US tended to say they liked events with loud noises more than people in other places; people in TH tended to disagree pretty strongly. (`sen_06`)
- People in CH and VT seemed to be more attuned to smelling flowers - especially interesting given that the CH sample was probably the most urban, and VT the most rural (calling **Josh**!). (`sen_07`) 
- Relatedly, but with a somewhat different pattern, people in the US tended to say they liked when others wore perfume, but people in CH and (as **Felicity** might have predicted!) responded more negatively to this.
- Unsurprisingly, people in VT had stronger responses to "walking barefoot on soft green grass".

**Josh**, you've gotta take a look at these with an eye toward a ratio! Maybe we should fold them into the "ratio of senses" doc...

This is just the tip of the iceberg. Tons to think through here.

# Distribution of responses for individual participants, by site

Another thing we might be interested in is how individual participants responded: Were there people who said yes to everything, or no to everything? How do these distributions of responses differ across participants in different sites?

Let's take a look:

```{r, fig.width = 6, fig.asp = 1}
d_long %>%
  filter(question %in% c("sen_01", "sen_02", "sen_03", "sen_04", "sen_05",
                         "sen_06", "sen_07", "sen_08", "sen_09", "sen_10",
                         "sen_11", "sen_12", "sen_13", "sen_14"),
         !grepl("attn", question),
         !is.na(response)) %>%
  left_join(question_key %>%
              distinct(question_label_universal, 
                       question_text,
                       byhand_coding,
                       byhand_subscale) %>%
              rename(question = question_label_universal,
                     coding = byhand_coding,
                     subscale = byhand_subscale)) %>%
  distinct() %>%
  mutate(response = factor(response),
         coding = factor(coding,
                         levels = c("-1", "1"),
                         labels = c("(REVERSED)", "")),
         question_text_short = gsub('(.{1,130})(\\s|$)',
                                    '\\1\n',
                                    paste0(substr(question_text,
                                                     start = 1, stop = 10000),
                                              # "...",
                                              coding)),
         subscale = factor(subscale, 
                           labels = c("Sensory seeking (Brown et al.)"))) %>%
  distinct() %>%
  count(ctry, subscale, subj, response) %>%
  spread(response, n) %>%
  mutate_at(vars(c(`-2`, `-1`, `0`, `1`, `2`)), funs(replace(., is.na(.), 0))) %>%
  mutate(total_n = `-2` + `-1` + `0` + `1` + `2`,
         prop_n2 = `-2`/total_n,
         prop_n1 = `-1`/total_n,
         prop_n0 = `0`/total_n,
         prop_p1 = `1`/total_n,
         prop_p2 = `2`/total_n,
         ctry = factor(ctry,
                       levels = c("us", "ghana", "thailand", 
                                  "china", "vanuatu"),
                       labels = c("US", "Ghana", "Thailand", 
                                  "China", "Vanuatu"))) %>%
  distinct() %>%
  select(-c(`-2`, `-1`, `0`, `1`, `2`)) %>%
  gather(response, prop, starts_with("prop")) %>%
  mutate(response = factor(response,
                           levels = c("prop_n2", "prop_n1", "prop_n0",
                                      "prop_p1", "prop_p2"),
                           labels = c("Strongly disagree", "Disagree", 
                                      "Neither agree nor disagree",
                                      "Agree", "Strongly agree"))) %>%
  ggplot(aes(x = prop, fill = ctry)) +
  facet_grid(response ~ ctry, scales = "free", space = "free") +
  geom_histogram(binwidth = 1/14) +
  scale_x_continuous(breaks = seq(0, 1, 0.25)) +
  scale_y_continuous(breaks = seq(0, 100, 10)) +
  scale_fill_brewer(palette = "Dark2") +
  theme_bw() +
  labs(title = "Distributions of how many times participants endorsed each response option for the 'Sensory seeking' (Brown et al.) scale items",
       x = "Proportion of responses (at the individual participant level)", y = "Count of participants", fill = "Site") +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))
```

Again, lots to chew on here, including:

- The vast majority of participants across sites - especially in the US - *never* used the most extreme negative response option, "Strongly disagree". This was also true for a sizable minority of participants in GH and VT, but most people used it once or more.
- This general pattern is also true (though less extreme) for the most extreme positive response option, "Strongly agree", though it seems like people in VT were more likely to use this option more frequently.
- There were a handful of people in the US, GH, and VT said "Strongly agree" for every (or almost every) question - but not a ton, and it's encouraging (re: comparable data quality across sites) that it also happened in the US. 

Again, lots to sort through here.

Just for fun, here's another way to look at the same data, overlaying the density distributions for each site on top of each other to see where they seem to be similar/different:

```{r, fig.width = 3, fig.asp = 3}
d_long %>%
  filter(question %in% c("sen_01", "sen_02", "sen_03", "sen_04", "sen_05",
                         "sen_06", "sen_07", "sen_08", "sen_09", "sen_10",
                         "sen_11", "sen_12", "sen_13", "sen_14"),
         !grepl("attn", question),
         !is.na(response)) %>%
  left_join(question_key %>%
              distinct(question_label_universal, 
                       question_text,
                       byhand_coding,
                       byhand_subscale) %>%
              rename(question = question_label_universal,
                     coding = byhand_coding,
                     subscale = byhand_subscale)) %>%
  distinct() %>%
  mutate(coding = factor(coding,
                         levels = c("-1", "1"),
                         labels = c("(REVERSED)", "")),
         question_text_short = gsub('(.{1,130})(\\s|$)',
                                    '\\1\n',
                                    paste0(substr(question_text,
                                                     start = 1, stop = 10000),
                                              # "...",
                                              coding)),
         subscale = factor(subscale, 
                           labels = c("Sensory seeking (Brown et al.)"))) %>%
  distinct() %>%
  count(ctry, subscale, subj, response) %>%
  spread(response, n) %>%
  mutate_at(vars(c(`-2`, `-1`, `0`, `1`, `2`)), funs(replace(., is.na(.), 0))) %>%
  mutate(total_n = `-2` + `-1` + `0` + `1` + `2`,
         prop_n2 = `-2`/total_n,
         prop_n1 = `-1`/total_n,
         prop_n0 = `0`/total_n,
         prop_p1 = `1`/total_n,
         prop_p2 = `2`/total_n,
         ctry = factor(ctry,
                       levels = c("us", "ghana", "thailand", 
                                  "china", "vanuatu"),
                       labels = c("US", "Ghana", "Thailand", 
                                  "China", "Vanuatu"))) %>%
  distinct() %>%
  select(-c(`-2`, `-1`, `0`, `1`, `2`)) %>%
  gather(response, prop, starts_with("prop")) %>%
  mutate(response = factor(response,
                           levels = c("prop_n2", "prop_n1", "prop_n0",
                                      "prop_p1", "prop_p2"),
                           labels = c("Strongly disagree", "Disagree", 
                                      "Neither agree nor disagree",
                                      "Agree", "Strongly agree"))) %>%
  ggplot(aes(x = prop, fill = ctry)) +
  facet_grid(response ~ ., scales = "free", space = "fixed") +
  geom_density(alpha = 0.3) +
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.25)) +
  scale_fill_brewer(palette = "Dark2") +
  theme_bw() +
  labs(title = "Distributions of how many times participants endorsed each\nresponse option for the 'Sensory seeking' (Brown et al.) scale items",
       x = "Proportion of responses (at the individual participant level)", y = "Count of participants", fill = "Site") +
  theme(legend.position = "top",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))
```

